Using a Rover's Active Suspension System as a 2-Axis Solar Tracker Mechanism

### 2020-06-24 extended_abstract.tex
sync with overleaf

@@

\begin{abstract}
The SherpaTT rover is prepared for further autonomous long distance traverses in terrain akin to the Martian environment. However, it features a fueled power generator which cannot be employed in extra-terrestial scenarios. As the rover is meant to approach a higher technology readiness level, a photovoltaic power subsystem is proposed to guide future design iterations. This paper presents the solar array sizing, design, and integration processes considered for two Martian mission sites: Iani Chaos at \SI{2}{\degree}S and Ismenius Cavus at \SI{34}{\degree}N. An alternative use case for the active suspension system is presented so that the proposed solar arrays may be inclined and oriented into power generating configurations that are more favorable than those achieved with passive suspension rovers. This results in traverse gains of up to \SI{34}{\percent} and \SI{25}{\percent} for clear days at Iani Chaos and Ismenius Cavus, respectively.
\end{abstract}

% Table of content is not needed.
% \tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The exploration rover SherpaTT has a total mass of approximately \SI{206}{\kilo\gram} and the legs as well as the \ac{RA} weigh about \SI{25}{\kilo\gram} each. The wheeled-leg active suspension system allows the rover to assume different poses with varying inertial moments. The rover is one of many systems comprising a \ac{MRS} developed at the \ac{DFKI}'s \ac{RIC}.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=3.2in]{figures/images/sherpatt-actively-articulated-suspension-sytem.png}\\
  \caption{Description of DoF present in SherpaTT’s
suspension system and placement of force-torque sensor}
  \label{fig:sherpatt-actively-articulated-suspension-system}
\end{figure}

The actively articulated suspension system consists of four wheeled-legs with a total of 20 motors. Motor distribution across a single leg is shown in \refFig{fig:sherpatt-actively-articulated-suspension-system}. Each leg is equipped with three suspension motors and two drive motors. The suspension motors are responsible for Pan, \ac{IL}, and \ac{OL} revolute joint rotations whereas the drive motors are responsible for \ac{WS} and \ac{WD}. A first design iteration of the rover with \ac{SA} for an Ismenius Cavus deployment is shown in \refFig{fig:solar-array-on-ismenius-cavus-chaos}.

\begin{figure}[h]
 \centering
 \includegraphics[width=2.8in]{figures/images/ismenius-cavus-10deg-pitch.png}\\
 \caption{Rover with \ac{SA} for Ismenius Cavus deployment.}
 \label{fig:solar-array-on-ismenius-cavus-chaos}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Power Budget}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Large inclination angles are typically preferred with respect to increased insolation for a sun-facing surface. However, constraints on the rover's active suspension system impose a limit on the achievable body pitch angle. Body pitch commands of up to \SI{10}{\degree} are experimentally evaluated during steep slope climbing in \cite{Cordes2018a}. Modeling higher pitch angles resulted in poor wheel-ground contact angle due to the \ac{WS} axis having the same tilt as the rover's body. The attainable tilt is thus restricted resulting in a maximum \ac{SA} surface inclination angle of $\beta = \SI{10}{\degree}$.

\input{tables/insolation-iani-chaos-clear-and-dusty-days.tex}

\refTab{tab:insolation-iani-chaos-clear-and-dusty-days} and \refTab{tab:insolation-ismenius-cavus-clear-and-dusty-days} present the best and worst case daily insolations $H_{h}$, on horizontal \ac{SA} surface, compared to those obtained with $H_{\beta}$, on an inclined sun-facing \ac{SA} surface. Optical depths $\tau$ for clear to dusty days are evaluated with the daily insolations expressed in \si{Wh.m^{-2}} and the gains in percentage. The solar insolation values are taken from \cite{Labreche2020} and obtained with Mars solar radiation formulas in \cite{Appelbaum1989}, \cite{Appelbaum1990}, \cite{Appelbaum1991}, \cite{Appelbaum1993}, and \cite{Appelbaum1994}.

\input{tables/insolation-ismenius-cavus-clear-and-dusty-days.tex}

Daily insolation gains obtained with an inclined surface are more pronounced for sites further away from the equator. For a typical optical depth of $\tau$ factor 0.4, the average daily insolation gain on the inclined surface is approximately \SI{7}{\percent} at Iani Chaos and \SI{9}{\percent} at Ismenius Cavus.
The mostly diffuse composition of solar irradiance at higher optical depths make inclined surfaces irrelevant in global dust storms. For $\tau \geq 2$, gains in daily insolation become negligible at both sites.

\input{tables/power-budget-hibernation-sol.tex}

As a prerequisite to \ac{SA} sizing, power budgets are defined for hibernation and flat terrain traverse reference Sols. These are presented in \refTab{tab:hibernation-sol-power-budget} and \refTab{tab:worst-case-traverse-sol-power-budget}. Hibernation power draws are identical during day and nighttime so the hibernation reference Sol does not have a best or worse case Sol with respect to available sunlight.

Durations of daylight dependent modes in the traverse reference Sol are based on the total length of daylight time for worst case daily insolations Sols presented in \refTab{tab:insolation-iani-chaos-clear-and-dusty-days} and \refTab{tab:insolation-ismenius-cavus-clear-and-dusty-days} with $\tau$ factor 1 and $\beta=\SI{10}{\degree}$ for the \ac{SA} surface inclination angle. Propulsion power draws for the rover's flat terrain traverse mode is determined from data collected during the SherpaTT Utah field trial \cite{Cordes2018b}.

\input{tables/worst-case-power-budget-flat-traverse-sol-tau-1.tex}

The \textit{Optimal Pose} mode in \refTab{tab:worst-case-traverse-sol-power-budget} consists of using the rover's active suspension system to reconfigure the \ac{SA} surface orientation and inclination so that daily insolation is maximized on the following Sol. In this manner, the suspension system undertakes the role of a 2-axis solar tracking mechanism.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Solar Array Sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The solar cell coverage area $A$ is expressed as:

\begin{equation}
  \label{eq:solar_cell_coverage_area}
  A = \frac{E}{\eta \cdot H \cdot PR}
\end{equation}

where $E$ is the rover's energy requirement, $\eta$ is the solar cell efficiency, $H$ is the daily insolation, and $PR$ is the solar cell performance ratio. An initial \ac{SA} sizing is determined with $H_{\beta}$ from \refTab{tab:insolation-iani-chaos-clear-and-dusty-days} and \refTab{tab:insolation-ismenius-cavus-clear-and-dusty-days} as well as $E$ from \refTab{tab:worst-case-traverse-sol-power-budget} for the worst case daily insolation at $\tau$ factor 1. \ac{EOL} values for $PR$ and $\eta$ are determined in \cite{Labreche2020}:

\begin{itemize}
  \item [(1)] $H$\,$=$\,\SI{2479}{Wh.m^{-2}} and $E$\,$=$\,\SI{775}{\watt\hour} at Iani Chaos.
  \item [(2)] $H$\,$=$\,\SI{1345}{Wh.m^{-2}} and $E$\,$=$\,\SI{750}{\watt\hour} at Ismenius Cavus.
  \item [(3)] $PR_{EOL}$\,$=$\,0.62.
  \item [(4)] $\eta_{EOL}$\,$=$\,0.22.
\end{itemize}

Furthermore, the solar cell packing efficiency is assumed at \SI{85}{\percent}, the \ac{SA} surface density at \SI{3.7}{kg.m^{-2}}, and the average slippage at \SI{15}{\percent} when traversing a flat terrains for any given distance. Traversing is constrained to daylight hours and it is assumed that on average traversing only occurs every third Sol.

At Iani Chaos, the required \ac{SA} area is \SI{2.7}{m^{2}} and the mass 9.95 \si{\kilo\gram}. \ac{SA} surface inclination of \SI{10}{\degree} with a daily sun-facing reorientation results in a \ac{SA} size decrease of \SI{3.9}{\percent} when compared against a horizontal surface configuration. The maximum flat traverse distance achievable over the course of a Martian year is increased by \SI{13.22}{\percent} from \SI{42.43}{\kilo\meter} to \SI{48.04}{\kilo\meter} with $\tau$ factor 1 during global dust storm season and 0.4 otherwise. At Ismenius Cavus, the required \ac{SA} area is \SI{4.8}{m^{2}}, its mass 17.8 \si{\kilo\gram}, and a \SI{4.6}{\percent} \ac{SA} size decrease is achieved. The maximum flat traverse distance achievable over the course of a Martian year is increased by \SI{2.13}{\percent} from \SI{63.05}{\kilo\meter} to \SI{64.39}{\kilo\meter}.

The traverse distance gains attributed to \ac{SA} inclination capabilities do not justify taking advantage of the rover's active suspension system for the purpose of increasing solar power generation. This is particularly true at Ismenius Cavus. The savings in \ac{SA} size and mass also leave much to be desired. Furthermore, the large \ac{SA} are problematic in terms of rover integration. This is illustrated in \refFig{fig:sa-area-initial-sizes}.

\begin{figure}[h]
  \centering
  \includegraphics[width=3.25in]{figures/images/sa-area-initial-sizes.png}\\
  \caption{Initial \ac{SA} sizing. The outlined square areas are equivalent to \ac{SA} areas of \SI{2.7}{m^{2}} for Iani Chaos and \SI{4.8}{m^{2}} for Ismenius Cavus.}
  \label{fig:sa-area-initial-sizes}
\end{figure}

To explain the lack of significant gains, the generated \ac{SA} energy and maximum traverse durations are plotted in \refFig{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations} for Ismenius Cavus. During clear days at $\tau$ factor 0.4, a ceiling is imposed on the daily maximum traverse durations due to the available daylight time for traversing. The maximum traverse time is already attained with a horizontal \ac{SA}, making an inclined \ac{SA} irrelevant in terms traverse distance gains. As seen in \refFig{fig:plot:sub:ismenius-cavus-max-traverse-durations}, the inclined \ac{SA} is only slightly advantageous during the global dust storm season with a $\tau$ factor of 1.

\begin{figure}[h]
\captionsetup[subfigure]{justification=centering}
  \centering
  \setlength{\subfigureWidth}{0.24\textwidth}
  \setlength{\graphicsHeight}{40mm}
  \begin{subfigure}[t]{\subfigureWidth}
    \centering
    \includegraphics[height=\graphicsHeight]{figures/plots/ismeniuscavus-daily-generated-energy-for-solar-cell-coverage-area-41m2.png}
    \subcaption{Generated Energy}
    \label{fig:plot:sub:ismenius-cavus-generated-energy}
  \end{subfigure}\hfill
  \begin{subfigure}[t]{\subfigureWidth}
    \centering
    \includegraphics[height=\graphicsHeight]{figures/plots/ismeniuscavus-75w-max-traverse-durations-for-solar-cell-coverage-area-41m2.png}
    \subcaption{Maximum Traverse Durations}
    \label{fig:plot:sub:ismenius-cavus-max-traverse-durations}
  \end{subfigure}
  \caption{Generated energy and maximum flat terrain traverse duration at Ismenius Cavus with solar cell coverage area of \SI{4.1}{m^{2}}. Surface inclination angle $\beta$ is \SI{10}{\degree}. $\tau$ factor 1 is used for global dust storm season ($\SI{185}{\degree} \leq L_{s} \leq \SI{315}{\degree}$) and 0.4 otherwise. The \textit{available daylight traverse time} corresponds to the amount of daylight hours left in a \textit{Traverse Sol} after subtracting the time taken by rover modes unrelated to traversing.}
  \label{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations}
\end{figure}

However, no such ceiling can be observed for Iani Chaos in \refFig{fig:plot:iani-chaos-generated-energy-and-max-traverse-durations} which would explain the poor gains for that mission site scenario. In both cases, lack of traverse distance gains is more closely tied to the $\tau$ factor selected when defining the worst case reference Sol that drives \ac{SA} sizing. At high optical opacities, increased light scattering by airborne Martian dust results in $H_{\beta} \approx H_{h}$ due to diffuse insolation being the largest component in the global insolation. Thus, when \ac{SA} sizing for power generation during dusty Sols, the resulting inclined \ac{SA} surface yield little to no benefits over horizontal surfaces with respect to traverse distance gains as well as \ac{SA} mass and area.

\begin{figure}[h]
\captionsetup[subfigure]{justification=centering}
  \centering
  \setlength{\subfigureWidth}{0.24\textwidth}
  \setlength{\graphicsHeight}{40mm}
  \begin{subfigure}[t]{\subfigureWidth}
    \centering
    \includegraphics[height=\graphicsHeight]{figures/plots/ianichaos-daily-generated-energy-for-solar-cell-coverage-area-23m2.png}
    \subcaption{Generated Energy}
    \label{fig:plot:sub:iani-chaos-generated-energy}
  \end{subfigure}\hfill
  \begin{subfigure}[t]{\subfigureWidth}
    \centering
    \includegraphics[height=\graphicsHeight]{figures/plots/ianichaos-75w-max-traverse-durations-for-solar-cell-coverage-area-23m2.png}
    \subcaption{Maximum Traverse Durations}
    \label{fig:plot:sub:iani-chaos-max-traverse-durations}
  \end{subfigure}
  \caption{Generated energy and maximum flat terrain traverse duration at Iani Chaos with solar cell coverage area of \SI{2.3}{m^{2}}. The same considerations were taken as in \refFig{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations}.}
  \label{fig:plot:iani-chaos-generated-energy-and-max-traverse-durations}
\end{figure}

The worst case power budget in \refTab{tab:worst-case-traverse-sol-power-budget} is set aside and the \ac{SA} sizing process is approached inversely by identifying solar cell coverage area targets based on the traverse distance gains brought about by an inclined surface. \refFig{fig:plot:flat-traverse-gains-for-different-sa-area} compares the traverse distance gains obtained with an inclined \ac{SA} surface for different solar cell coverage areas and optical depths.

\begin{figure}[h]
\captionsetup[subfigure]{justification=centering}
  \centering
  \setlength{\subfigureWidth}{0.24\textwidth}
  \setlength{\graphicsHeight}{40mm}
    \begin{subfigure}[t]{\subfigureWidth}
      \centering
      \includegraphics[height=\graphicsHeight]{figures/plots/ianichaos-75w-traverse-gains-for-different-solar-cell-coverage-areas.png}
    \subcaption{Iani Chaos}
    \label{fig:plot:sub:ismenius-chaos-flat-traverse-gains-for-different-sa-area}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{\subfigureWidth}
      \centering
      \includegraphics[height=\graphicsHeight]{figures/plots/ismeniuscavus-75w-traverse-gains-for-different-solar-cell-coverage-areas.png}
    \subcaption{Ismenius Cavus}
    \label{fig:plot:sub:iani-chaos-flat-traverse-gains-for-different-sa-area}
    \end{subfigure}
    \caption{Average flat terrain traverse distance gains at mission sites for different solar cell coverage areas. \ac{SA} inclination angle $\beta_{max} = \SI{10}{\degree}$ with orientation angles $\gamma_{c}$ set to their optimal values for the considered traverse Sols.}
    \label{fig:plot:flat-traverse-gains-for-different-sa-area}
\end{figure}

Targeting a solar cell coverage area of \SI{1.5}{m^{2}} at Iani Chaos results in an average \SI{34}{\percent} gain in traverse for a clear day at $\tau$ factor 0.4. The gain remains significant at \SI{23}{\percent} for a dusty day at $\tau$ factor 1. The increase in gain observe for $\tau$ factors greater than 1 are inconsequentially tied to negligible distances. At Ismenius cavus, a solar cell coverage area of \SI{2.4}{m^{2}} results in \SI{25}{\percent} and \SI{10}{\percent} gains for $\tau$ factor 0.4 and 1, respectively. Applying the same packing efficiency and \ac{SA} surface density as the initial sizing results in \ac{SA} areas of \SI{1.7}{m^{2}} at Iani Chaos with a mass of \SI{6.3}{\kilo\gram} and \SI{2.8}{m^{2}} at Ismenius Cavus with a mass of \SI{10.4}{\kilo\gram}. The maximum daily traverse durations attainable at both sites with these target \ac{SA} areas are shown in \refFig{fig:plot:final-maximum-traverse-durations-at-missions-sites}. However, these gains come with significantly reduced maximum flat traverse distance coverage of \SI{12}{\kilo\meter} at Iani Chaos and \SI{35}{\kilo\meter} at Ismenius Cavus. Mission design with or without \ac{SA} surface inclination thus not only depend on \ac{SA} size and mass constraints but also on mission requirements with respect to target traverse coverages.

\begin{figure}[h]
\captionsetup[subfigure]{justification=centering}
  \centering
  \setlength{\subfigureWidth}{0.24\textwidth}
  \setlength{\graphicsHeight}{40mm}
  \begin{subfigure}[t]{\subfigureWidth}
    \centering
    \includegraphics[height=\graphicsHeight]{figures/plots/ianichaos-75w-max-traverse-durations-for-solar-cell-coverage-area-15m2.png}
    \subcaption{Iani Chaos, solar cell coverage = \SI{1.5}{m^{2}}}
    \label{fig:plot:sub:final-maximum-traverse-durations-iani-chaos}
  \end{subfigure}\hfill
  \begin{subfigure}[t]{\subfigureWidth}
    \centering
    \includegraphics[height=\graphicsHeight]{figures/plots/ismeniuscavus-75w-max-traverse-durations-for-solar-cell-coverage-area-24m2.png}
    \subcaption{Ismenius Cavus, solar cell coverage area = \SI{2.4}{m^{2}}}
    \label{fig:plot:sub:final-maximum-traverse-durations-ismenius-cavus}
  \end{subfigure}
  \caption{Maximum traverse durations at mission sites. The same considerations were taken as in \refFig{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations}.}
  \label{fig:plot:final-maximum-traverse-durations-at-missions-sites}
\end{figure}

\ac{SA} sizing with the hibernation reference Sol power budget defined in \refTab{tab:hibernation-sol-power-budget} as the worst case power budget fails to meet the target \ac{SA} areas. However, the required power draws only differ by a few Watts. At Iani Chaos, this is achieved by reducing the hibernation mode power draws from \SI{18}{\watt} to \SI{17}{\watt}. At Ismenius Cavus, hibernation power draws need to be reduced from \SI{18}{\watt} to \SI{15}{\watt}. Taking into account a \SI{20}{\percent} system margin, the energy requirement for hibernation Sols become \SI{490}{\watt\hour} at Iani Chaos for a \SI{1.7}{m^{2}} \ac{SA} area and \SI{432}{\watt\hour} at Ismenius Cavus for a \SI{2.8}{m^{2}} \ac{SA} area. \refFig{fig:rover-body-redesign} shows the rover's body redesign from a pyramid to a cubic shape in order to better accommodate the \ac{SA} surface and avoid shadowing.

\begin{figure}[h]
\captionsetup[subfigure]{justification=centering}
  \centering
  \setlength{\subfigureWidth}{0.24\textwidth}
  \setlength{\graphicsHeight}{29mm}
  \begin{subfigure}[t]{\subfigureWidth}
    \centering
    \includegraphics[height=\graphicsHeight]{figures/images/body-before.png}
    \subcaption{Before}
    \label{fig:sub:rover-body-redesign-before}
    \end{subfigure}\hfill
  \begin{subfigure}[t]{\subfigureWidth}
    \centering
    \includegraphics[height=\graphicsHeight]{figures/images/body-after.png}
    \subcaption{After}
    \label{fig:sub:rover-body-redesign-after}
  \end{subfigure}
  \caption{Rover body redesign.}
  \label{fig:rover-body-redesign}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The proposed rover and \ac{SA} configurations are modeled with Blender/Phobos and loaded into MARS for mission scenario simulation. Phobos is ``an add-on for the open-source 3D modeling software Blender that enables the creation of robot models for use in robot frameworks like ROS and ROCK or in real-time simulations such as MARS'' \cite{Phobos}. MARS is ``a cross-platform simulation and visualization tool created for robotics research. It consists of a core framework containing all main simulation components, a GUI (based on Qt), 3D visualization (using OSG) and a physics engine (based on ODE)'' \cite{MARSSim}.

\subsection{Z-Axis Revolutions}

\refFig{fig:sub:simulation-data-rover-revolution-generated-power-line-chart} and \refFig{fig:sub:simulation-data-rover-revolution-generated-power-polar-chart} are two different representations of the same solar power output obtained from commanding the rover to execute a \SI{10}{\degree} forward body-pitch followed by several revolutions around its z-axis. These revolutions result in a sinusoidal power output variation. Local spikes and dips are noted around \SI{100}{\second} and \SI{160}{\second} due to small changes in the \ac{SA} inclination and orientation angles caused by the rover driving over uneven terrain. In \refFig{fig:sub:simulation-data-rover-revolution-generated-power-polar-chart}, the angle values represent the direction faced by the inclined \ac{SA}. Maximum power is generated when the \ac{SA} is oriented southwards, towards the equator, in the general direction of the sun. Inversely, facing northwards, away from the sun, generates the least amount of power. These are the expected results thus validating the simulation environment for further development and mission scenario analysis.

\begin{figure}[h]
  \captionsetup[subfigure]{justification=centering}
  \centering
  \setlength{\subfigureWidth}{0.24\textwidth}
  \setlength{\graphicsHeight}{40mm}
  \begin{subfigure}[t]{\subfigureWidth}
    \centering
    \includegraphics[height=\graphicsHeight]{figures/plots/zaxis-revolutions.png}
    \subcaption{Line chart}
    \label{fig:sub:simulation-data-rover-revolution-generated-power-line-chart}
  \end{subfigure}\hfill
  \begin{subfigure}[t]{\subfigureWidth}
    \centering
    \includegraphics[height=\graphicsHeight]{figures/plots/zaxis-revolutions-polar.png}
    \subcaption{Polar chart}
    \label{fig:sub:simulation-data-rover-revolution-generated-power-polar-chart}
  \end{subfigure}\\[0.6ex]
  \caption{Power generated by the rover's \ac{SA} for multiple revolutions along its z-axis. Simulation condition is solar noon at Ismenius Cavus with $\beta \approx \SI{10}{\degree}$. In the polar chart, angle values represent the direction faced by the inclined \ac{SA} where \SI{0}{\degree} is South (towards the equator), \SI{-90}{\degree} is East, \SI{180}{\degree} is North, and \SI{90}{\degree} is West.}
  \label{fig:simulation-data-rover-revolution-generated-power}
\end{figure}

\subsection{Slope Compensation}

The worst case slope traverse is on an inclined surface facing away from the sun. The rover's active suspension system can be used to reduce the \ac{SA} inclination angle by commanding a rover body pitch in the opposite direction. This slope compensation scenario is illustrated in \refFig{fig:sub:rover-on-slope-beta} where $B$ denotes the slope surface inclination angle and $\beta$ the \ac{SA} surface inclination angle.

\begin{figure}[h]
\captionsetup[subfigure]{justification=centering}
  \centering
  \begin{subfigure}[t]{\subfigureWidth}
    \centering
    \includegraphics[height=\graphicsHeight]{figures/images/stick-rover-beta-large.png}
    \subcaption{$\beta = B$}
    \label{fig:sub:rover-on-slope-beta-large}
  \end{subfigure}\hfill
  \begin{subfigure}[t]{\subfigureWidth}
    \centering
    \includegraphics[height=\graphicsHeight]{figures/images/stick-rover-beta-small.png}
    \subcaption{$\beta < B$}
    \label{fig:sub:rover-on-slope-beta-small}
  \end{subfigure}
  \caption{Slope compensation with active suspension system to reduce the \ac{SA} surface inclination angle. Slope inclination angle $B = \SI{30}{\degree}$. In (a), $\beta = B = \SI{30}{\degree}$. In (b), the rover is tilted \SI{10}{\degree} in the opposite direction of the slope so that $\beta = \SI{20}{\degree}$.}
  \label{fig:sub:rover-on-slope-beta}
\end{figure}

By way of example, at Ismenius Cavus for a $\tau$ factor of 0.4 and an areocentric longitude $L_{s}$ of \SI{270}{\degree}, descending a \SI{30}{\degree} slope bearing North results in a daily insolation of \SI{319}{Whm^{-2}}. This is increased to \SI{767}{Whm^{-2}} by decreasing $\beta$ from \SI{30}{\degree} to \SI{25}{\degree} after tilting the rover southwards by \SI{5}{\degree} so that $\beta < B$. A \SI{10}{\degree} tilt would increase the daily insolation to \SI{1046}{Whm^{-2}} with $\beta = \SI{20}{\degree}$. The solar power generated from this scenario is simulated. \refFig{fig:sub:rover-on-slope-beta} shows solar power outputs for different body-pitch configuration while the rover is on a \SI{30}{\degree} slope. The initial state of the \ac{SA} surface inclination angle is equal to that of the slope angle. Two separate \SI{5}{\degree} forward pitch increments are executed at \SI{25}{\second} and \SI{35}{\second} which worsen solar power output by changing the \ac{SA} surface inclination angle from $\sim$\SI{30}{\degree} to $\sim$\SI{40}{\degree}. Four separate \SI{5}{\degree} backward pitch decrements are executed from \SI{45}{\second} to \SI{65}{\second}, progressively improving power generation as $\beta$ is decreased from $\sim$\SI{40}{\degree} to $\sim$\SI{20}{\degree}. As a final task, the rover is commanded to drive forward at \SI{80}{\second} and it encounters uneven terrain which introduces minor fluctuations to the solar power output.

\begin{figure}[h]
  \centering
  \includegraphics[width=3.25in]{figures/plots/slope-compensation.png}
  \caption{Slope compensation with active suspension system to reduce the \ac{SA} surface inclination angle. Slope inclination angle $B = \SI{30}{\degree}$. In (a), $\beta = B = \SI{30}{\degree}$. In (b), the rover is tilted \SI{10}{\degree} in the opposite direction of the slope so that $\beta = \SI{20}{\degree}$.}
  \label{fig:sub:rover-on-slope-beta}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The findings of this paper support using the SherpaTT rover active suspension system as a mechanism for solar panel inclination and orientation under certain \ac{SA} sizing conditions. Combining a maximum attainable \ac{SA} surface inclination angle of \SI{10}{\degree} with optimal daily orientation angles results in appreciable traverse gains when compared to what is obtained from a horizontal surface. However, this is not true for large \ac{SA} areas. Furthermore, the smaller the required solar cell coverage area the greater the gains. In light of this, \ac{SA} sizing for the the worst case daily insolations introduce a hibernation mode solar power draw constraint of \SI{17}{\watt} near the equator at \SI{2}{\degree}S and \SI{15}{\watt} in the northern hemisphere at \SI{34}{\degree}N. With these power budgets, an average traverse gain of \SI{34}{\percent} is achieved at \SI{2}{\degree}S for a clear day with a $\tau$ factor of 0.4. At \SI{34}{\degree}N, the average gain is \SI{25}{\percent} under the same atmospheric opacity. These gains remain significant on dusty days at \SI{23}{\percent} and \SI{10}{\percent} at respective latitudes with a $\tau$ factor of 1.

>>>>

% For block commenting
\newcommand{\comment}[1]{}

@@

The SherpaTT rover is prepared for further autonomous long distance traverses in terrain akin to the Martian environment. However, it features a fueled power generator which cannot be employed in extra-terrestial scenarios. As the rover is meant to approach a higher technology readiness level, a photovoltaic power subsystem is proposed to guide future design iterations. This paper presents the solar array sizing, design, and integration processes considered for two Martian mission sites: Iani Chaos at \SI{2}{\degree}S and Ismenius Cavus at \SI{34}{\degree}N. An alternative use case for the active suspension system is presented so that the proposed solar arrays may be inclined and oriented into power generating configurations that are more favorable than those achieved with passive suspension rovers. This results in traverse gains of up to \SI{34}{\percent} and \SI{25}{\percent} for clear days at Iani Chaos and Ismenius Cavus, respectively.

The exploration rover SherpaTT has a total mass of approximately \SI{206}{\kilo\gram} and the legs as well as the \ac{RA} weigh about \SI{25}{\kilo\gram} each. The wheeled-leg active suspension system allows the rover to assume different poses with varying inertial moments. The rover is one of many systems comprising a \ac{MRS} developed at the \ac{DFKI}'s \ac{RIC}.

@@

\comment{
\begin{figure}[h]
  \centering
  \includegraphics[width=3.2in]{figures/images/sherpatt-actively-articulated-suspension-sytem.png}\\
  \caption{Description of DoF present in SherpaTT’s
suspension system and placement of force-torque sensor}
  \label{fig:sherpatt-actively-articulated-suspension-system}
\end{figure}
}

The active suspension system consists of four wheeled-legs with a total of 20 motors.\comment{Motor distribution across a single leg is shown in \refFig{fig:sherpatt-actively-articulated-suspension-system}.} Each leg is equipped with three suspension motors and two drive motors. The suspension motors are responsible for Pan, \ac{IL}, and \ac{OL} revolute joint rotations whereas the drive motors are responsible for \ac{WS} and \ac{WD}. \comment{A first design iteration of the rover with \ac{SA} for an Ismenius Cavus deployment is shown in \refFig{fig:solar-array-on-ismenius-cavus-chaos}.}

\comment{
\begin{figure}[h]
 \centering
 \includegraphics[width=2.8in]{figures/images/ismenius-cavus-10deg-pitch.png}\\
 \caption{Rover with \ac{SA} for Ismenius Cavus deployment.}
 \label{fig:solar-array-on-ismenius-cavus-chaos}
\end{figure}
}

@@

The findings of this paper support using the SherpaTT rover active suspension system as a mechanism for solar panel inclination and orientation under certain \ac{SA} sizing conditions. Combining a maximum attainable \ac{SA} surface inclination angle of \SI{10}{\degree} with optimal daily orientation angles results in appreciable traverse gains when compared to what is obtained from a horizontal surface. However, this is not true for large \ac{SA} areas. Furthermore, the smaller the required solar cell coverage area the greater the gains. In light of this, \ac{SA} sizing for the the worst case daily insolations introduce a hibernation mode solar power draw constraint of \SI{17}{\watt} near the equator at \SI{2}{\degree}S and \SI{15}{\watt} in the northern hemisphere at \SI{34}{\degree}N. \comment{With these power budgets, an average traverse gain of \SI{34}{\percent} is achieved at \SI{2}{\degree}S for a clear day with a $\tau$ factor of 0.4. At \SI{34}{\degree}N, the average gain is \SI{25}{\percent} under the same atmospheric opacity. These gains remain significant on dusty days at \SI{23}{\percent} and \SI{10}{\percent} at respective latitudes with a $\tau$ factor of 1.}
